---
title: " "
author: " "
date: " "
output: pdf_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(biostat3)
library(survival)
library(tidyverse)
library("ggfortify")
library(survminer)
library(kableExtra)
```

# Question 3

```{r}
data = ovarian %>% mutate(fustat = as.factor(fustat), rx = as.factor(rx))
```

### 1. Create life-time stratified by rx
```{r}
# Create life-table stratified by rx
lt1 = lifetab2(Surv(futime, fustat == 1) ~ 1, 
               data[data$rx == 1, ], 
               breaks= seq(0, 1300, 100)) #rx=1
lt2 = lifetab2(Surv(futime, fustat == 1) ~ 1, 
               data[data$rx == 2, ], 
               breaks= seq(0, 1300, 100)) #rx=2
options(digits=2)
print(lt1) # life-table for treatment 1
print(lt2) # life-table for treatment 2
```

### 2. Plot harzard function by rx

```{r warning=FALSE}
ggplot(lt1, aes(x = tstart, xend = tstop, y = hazard, yend = hazard)) +
  geom_segment() +
  labs(x = "t", y = "h(t)") +
  ggtitle("Hazard function for treatment 1") +
  theme_minimal() #rx=1

ggplot(lt2, aes(x = tstart, xend = tstop, y = hazard, yend = hazard)) +
  geom_segment() +
  labs(x = "t", y = "h(t)") +
  ggtitle("Hazard function for treatment 2")+
  theme_minimal() #rx=2
```

### 3. Plot K-M survival function by rx

```{r warning=FALSE}
mfit = survfit(Surv(futime, fustat == 1) ~ rx, data)
plot(mfit, ylab="S(t)", xlab="Time in days",
     main = "Kaplan−Meier estimates of treatment-specific survival")
```

### 4. Median for each treatment group

- rx 1: median = 638
- rx 2: median doesn't exist

```{r warning=FALSE}
print(mfit)
```
 
### 5. Compare survival function estimations between K-M and F-H methods

```{r warning=FALSE}
hfit = survfit(Surv(futime, fustat == 1) ~ rx, type = "fleming-harrington", data)
print(hfit)
summary(mfit)
summary(hfit)
mfit %>% autoplot() + ylab("S(t)") + xlab("Time")
hfit %>% autoplot() + ylab("S(t)") + xlab("Time")
```

The two methods give the same median estimations. Generally the F-H method gave higher survival rates and lower se, which could be because the di/ni rate is rather high in this dataset. 

The survival rate of patients in treatment 1 is lower than those in treatment 2, especially in the first 300 days,indicating treatment 2 could potentially be a better treatment. In treatment 1 group, less than half the patients survived beyond 700 days, while in treatment 2 group, more than 57% patients survived beyond 1200 days.

