---
title: "HW6"
author: "Code Appendix"
date: "2023-11-13"
output: 
  pdf_document:
    number_sections: true
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(biostat3)
library(survival)
library(tidyverse)
library("ggfortify")
library(survminer)
library(kableExtra)
```


```{r chunk_2(a)}
data(pbc, package="survival")
data = pbc |> 
  mutate(time = time/30,
         status = ifelse(status != 0, 1, 0),
         edema = ifelse(edema == 0.5, 1, edema),
         sexn = case_when(sex == "m" ~ 1,sex == "f" ~ 0)) |> 
  drop_na()
s = coxph(Surv(time, status) ~ sexn + edema + bili + albumin + copper + ast + protime + stage, data)
base = data.frame(sexn = 0,
                  edema = 0,
                  bili = 0,
                  albumin = 0,
                  copper = 0,
                  ast = 0,
                  protime = 0,
                  stage = 1)
survival = basehaz(s, newdata = base) |> 
  mutate(survival = exp(-hazard)) |> 
  filter(survival >= 0.8976 & survival <= 0.9005) |> 
  knitr::kable()
```

```{r chunk_2(c)}
b = data.frame(sexn = 1,
               edema = 1,
               bili = median(data$bili),
               albumin = median(data$albumin),
               copper = median(data$copper),
               ast = median(data$ast),
               protime = median(data$protime),
               stage = 4)
survival_2 = basehaz(s, newdata = b) |> 
  mutate(survival = exp(-hazard)) |> 
  filter(survival >= 0.895 & survival <= 0.9005) |> 
  knitr::kable()
```


\newpage
## 

1. Potential confounding factors for the observed dose-response in efficacy: 
* First, identify potential confounding factors by:
imbalance baseline characteristics between two doses with a 1-side significant level of 0.05.
* Then, identify prognostic factors by:
test each factor individually by controlling the dose and keep significant factors as the confounding factors.
* Lastly, control all the selected confounding factors.

2. If there were any dose by baseline interactions.
Use Cox model to compare the survival function of different (independent) groups:
* Use a set of K covariates to represent the K+1 groups, select a reference group where k=0;
* Fit Cox model, and use likelihood ratio test for the results.


## 

### 
```{r}
survival
```
The survival time that 90% subjects survived for baseline survival function is 76.6 month.

### 
```{r}
survival_2
```
The survival time for male subjects who had edema and stage=4 and taking median for all other covariates in the model is 18.3 month.

\newpage

## 

**After backward selection, the variables I chose are:** 

**sex, edema, bili, albumin, copper, ast, protime, stage.**


* Here's the code for SAS:

libname mylib "/home/u61890905/EPG1V2";

proc import datafile="/home/u61890905/pbc.xlsx" 

out=pbc
            
dbms=xlsx replace;
            
run;

proc phreg data=pbc;

class trt sex;

model time*status(0)=trt sex

ascites hepato spiders edema

bili chol albumin copper

alk.phos ast trig platelet

protime stage

/selection=backward

slentry=0.25

slstay=0.15

details;

run;

